Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-13 paper/sheaf_lics.tex
add open modality, references to MM

\usepackage{enumerate}
\usepackage{wasysym}
\usepackage[all]{xy}
\def\dar[#1]{\ar@<2pt>[#1]\ar@<-2pt>[#1]}
\DeclareMathOperator{\Type}{Type}
\DeclareMathOperator{\HProp}{HProp}
\DeclareMathOperator{\nat}{nat}
\DeclareMathOperator{\Unit}{Unit}
\DeclareMathOperator{\im}{Im}
\DeclareMathOperator{\id}{id}
\newcommand{\modal}{\ensuremath{\ocircle}}

@@

@@

In homotopy type theory, we have 
$$X\times_Y \cdots\times_Y X = \sum_{x:X^n} (f x_1 = f x_2) \land
\cdots \land (f x_{n-1} = f x_n).$$
\begin{defi}
  If $f:X \to Y$ is a map, then the {\em \v{C}ech nerve} of $f$ is the
  diagram
  $$C(f) := \cdots
    X \times_Y X \times_Y X
   \underset{\longrightarrow}{\stackrel{\longrightarrow}{\longrightarrow}}
   X \times_Y X 
\stackrel{\longrightarrow}{\longrightarrow} X$$
with canonical projections.
\end{defi}

The Giraud axiom asserts that, if $f:X\to Y$ is a surjection, then the
colimit of $C(f)$ is $Y$. See~\cite{lurie}.

@@

We define sheaves by induction on the homotopical truncation level of types
~: we define sheaves in $\HProp$ as the classical types ({\em ie}
implied by their double negation), and
we define sheaves on $\Type_{n+1}$ {\em via} usual definition of sheaves,
as seen in~\cite{maclanemoerdijk} and sheaves on $\Type_n$. Of course,
the definition must be cumulative.

We will call $\mathcal S_i$ the universe of sheaves on $\Type_i$.

@@

We now need to show that $\square$ is universal. The following
lemma is central in the proof~:
\begin{lem}
  Let $T:\Type_{n+1}$. Then $\square T$ is the colimit of the closed
  diagonal diagram
  $$\cdots \overline{\Delta_3} \underset{\longrightarrow}{\stackrel{\longrightarrow}{\longrightarrow}}
   \overline{\Delta_2}
\stackrel{\longrightarrow}{\longrightarrow} \overline{\Delta_1},$$
where $\Delta_k$ is the $k$-pullback of $\id : T \to T$.
\end{lem}
\begin{proof}
  As $\mu_T$ is an embedding, we know by Giraud axiom that $\square T$ is the colimit
  of $C(\mu_T)$. If we can show that $C(\mu_T) = C(\id)$, the the
  result will follow.

>>>>

\usepackage{enumerate}
\usepackage{wasysym}
\usepackage[all]{xy}
\def\dar[#1]{\ar@<2pt>[#1]\ar@<-2pt>[#1]} %double arrows in xy
\def\tar[#1]{\ar@<2pt>[#1]\ar@<0pt>[#1]\ar@<-2pt>[#1]} %triple arrows in xy
\DeclareMathOperator{\Type}{Type}
\DeclareMathOperator{\HProp}{HProp}
\DeclareMathOperator{\nat}{nat}
\DeclareMathOperator{\Unit}{Unit}
\DeclareMathOperator{\im}{Im}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Contr}{Contr}
\newcommand{\modal}{\ensuremath{\ocircle}}

@@

Another useful property is that we can extend property {\it (iii)} to
dependent product.

@@

In homotopy type theory, we have 
$$X\times_Y \cdots\times_Y X = \sum_{x:X^n} (f x_1 = f x_2) \land
\cdots \land (f x_{n-1} = f x_n).$$
\begin{defi}
  If $f:X \to Y$ is a map, then the {\em \v{C}ech nerve} of $f$ is the
  diagram
  $$\xymatrix{
    C(f) := \cdots~ X \times_Y X \times_Y X \tar[r] & X \times_Y X \dar[r] & X
  }$$
with canonical projections.
\end{defi}

The Giraud axiom asserts that, if $f:X\to Y$ is a surjection, then the
colimit of $C(f)$ is $Y$. Viewing homotopy type theory as a
type-theoristic version of higher topos theory, it seems that this
axiom can be proved~\cite{lurie}, although we admit it in this paper.

@@

We will define sheaves by induction on the homotopical truncation level of types
~: the base case will be any left exact modality on $\HProp$, and we
give in this section some definitions useful for the inductive case.

@@

We now need to show that $\square$ is universal. The following
lemma is central in the proof~:
\begin{lem}
  Let $T:\Type_{n+1}$. Then $\square T$ is the colimit of the closed
  diagonal diagram
  $$\cdots \overline{\Delta_3} \underset{\longrightarrow}{\stackrel{\longrightarrow}{\longrightarrow}}
   \overline{\Delta_2}
\stackrel{\longrightarrow}{\longrightarrow} \overline{\Delta_1},$$
where $\Delta_k$ is the $k$-pullback of $\id : T \to T$.
\end{lem}

This lemma is an adaptation of the sheafification process
in~\cite{maclanemoerdijk}, where they consider only the kernel pair of
$\mu_T$ instead of the \v{C}ech nerve.

\begin{proof}
  As $\mu_T$ is an embedding, we know by Giraud axiom that $\square T$ is the colimit
  of $C(\mu_T)$. If we can show that $C(\mu_T) = C(\id)$, the the
  result will follow.
